Interactive dashboard to monitor the COVID-19 outbreak and Vaccine Administration

### 2022-05-15 manuscript_covid19dashboard.Rmd
Updated page with images

The "Sri Lanka COVID-19 Dashboard" provides an overview of the COVID-19 pandemic and administration of vaacine information in Sri Lanka. Figure 1 shows an screenshot of the dashboard. This dashboard has eight panels as listed in Table 6. The deployed dashboard is made accessible to public through https://thiyanga.netlify.app/post/covid19srilankadb/

```{r, echo=FALSE, fig.cap="Overview Panel: Screeshot of the Dashboard", out.width="80%", fig.align='center'}
knitr::include_graphics("images/dashboard.png")
```

@@

```{r, comment=NA, message=FALSE, warning=FALSE, fig.cap="Spatial DIstribution of COVID1-19 Cases by Districts"}

@@

```{r, echo=FALSE, fig.cap="Time Series Plot of Distribution of First Dose and Second Dose", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/d3.png")
```

```{r, echo=FALSE, fig.cap="Distribution of Vaccines by Different Types and Dose", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/d2.png")
```

@@

# Appendix: Overview of reviewed dashboard

Real time updated COVID-19 dashboard created by the John Hopkins University Center for Systems Science & Engineering (JHU CSSE) has included total confirmed cases & total deaths by country, province/region/state (not for all countries)[6]. Weekly & daily global confirmed cases, deaths & vaccine doses have been visualized using bar plots related to the date in the side panels. Also, an interactive world map has included in the dashboard to represent total confirmed cases, incidence rate, fatality ratio & vaccine doses administered by country & state of US. All the links related to the data sets has been included in the dashboard. In this dashboard red, white, green colors has been used to indicate confirmed cases, deaths & vaccine doses respectively. The dashboard has fitted on a single screen.

```{r, fig.cap="Johns Hopkins University COVID-19 Dashboard"}
knitr::include_graphics("Images/1.PNG")
```

Live updated “WHO COVID-19 dashboard” contained four panels. The interactive world
map in the dashboard has visualized the distribution of COVID-19 confirmed cases, deaths &
vaccination by country [15]. Line chart & bar charts have been used as visualization plots. Blue, red, green colors have been used to represent confirmed cases, deaths & vaccination respectively. The links related to the underlying data was available in the dashboard. The dashboard was not fitted on a single screen.

```{r, fig.cap="WHO COVID-19 Dashboard"}
knitr::include_graphics("Images/2.PNG")
```

The “COVID-19 surveillance dashboard” created by the University of Virginia in
collaboration with Bio complexity Institute has included interactive world map with a time slide to visualize the confirmed cases, recovered cases, deaths, active cases & vaccine details [7]. Line charts, bar charts & data tables have been visualized in the dashboard. Red, blue, green & yellow colors have been used to identify confirmed, deceased, recovered & active cases respectively. The data behind the dashboard also available on the dashboard & can be downloaded. The dashboard has fitted on a single screen.

```{r, fig.cap="COVID-19 Surveillance Dashboard"}
knitr::include_graphics("Images/3.PNG")
```

Corona cases (COVID-19) per municipality in Belgium dashboard has included interactive
map for distribution of total confirmed cases per municipality, bar chart for number of cases per province, line charts for number of cases per day by region & municipality, dodge bar chart for deaths per region, per age & pie chart for deaths per age as visualization methods[3]. Also it included several value boxes for total cases, total deaths & hospital situations. There was no specific color theme used in this dashboard. This dashboard also fitted on a single screen.

```{r, fig.cap="Corona cases per Municipality in Belgium Dashboard"}
knitr::include_graphics("Images/4.PNG")
```

The COVID-19 dashboard for England created by NHS providers included daily totals, daily changes & weekly changes in new cases, hospital admission, patients in hospital, and patients
in ICU beds, deaths & vaccinations in England as counts [2]. Bar plots for daily new cases, hospital admissions & deaths for last 30 days have been added in this dashboard. Also it has included data table for total count, daily changes (as increase or decrease), weekly changes (as increase or decrease) of new cases & hospital admission by region. It can be seen that, three different colors have been used in bar plot as orange for new cases, green for hospital admissions & red for deaths. These plots were not interactive plots & there was only one panel. The dashboard was not fitted on a single screen.

```{r, fig.cap="COVID-19 dashboard for England"}
knitr::include_graphics("Images/5.PNG")
```

The Environmental Science and Research Institute COVID-19 dashboard for New Zealand (was developed & is maintained in collaboration with Epi-interactive Ltd) contained five panels
as overview, outbreak, source, international & ESR reports [10]. In this real time updated dashboard, they have included value boxes for total confirmed cases, recovered cases, deaths & interactive map has been added for distribution of confirmed & probable cases as incidence & count. Also they have included bar charts for confirmed cases distribution by gender, age group, & line charts for confirmed & deaths as daily & cumulative. The dashboard has not fitted on a single screen.

```{r, fig.cap="New Zealand COVID-19 Dashboard"}
knitr::include_graphics("Images/6.PNG")
```

Pakistan’s official COVID-19 dashboard is a real time updated dashboard with one panel. This dashboard contains value boxes for total confirmed cases, active cases, deaths, recovered
cases by country. Province wise cases have been represented by map & data table [11]. Line charts & bar charts have been added to visualize the distribution of cases related to time & province. In the value boxes blue, orange, pink & green colors have been applied for confirmed cases, active cases, deaths & recoveries respectively, but there was no specific color theme used when plotting the graphs. The dashboard cannot be seen on a single screen without grid overlay.

```{r, fig.cap="COVID-19 Dashboard for Pakistan"}
knitr::include_graphics("Images/7.PNG")
```

COVID-19 Canada live dashboard has been developed with three panels for provincial data, hospital resources & projections [14]. This dashboard contained interactive map for represented total reported cases & deaths by province. Data tables, line charts, bar charts were the most frequently used visualization types of this dashboard. More details were presented on this dashboard by province like ventilator counts, hospital beds per 100 residents, resource capacity based on critical case rate, effect of social distance, forecast of deaths & cases. There was no specific color theme applied for plotting the graphs. The dashboard also was not fitted on a single screen.

```{r, fig.cap="COVID-19 in Canada dashboard"}
knitr::include_graphics("Images/8.PNG")
```

“Zoho analytics COVID-19 live dashboard” for India contained three panels as insight by state, trend analysis & vaccination [1]. Interactive country map has been used to visualize the distribution of confirmed cases, active cases, deaths, recovered cases & vaccination by states in India. Line charts, bar charts & doughnut shape pie charts have been used as other visualization tools. Also this dashboard contained data table for overview of COVID-19 in India. This dashboard also was not fitted on a single screen.

```{r, fig.cap="India COVID-19 Dashboard"}
knitr::include_graphics("Images/9.PNG")
```

Italy COVID-19 dashboard created by the COVID-19 task force of the department of infection diseases and the IT service Istituto Superiore Sanita, contained interactive map, bar charts, doughnut shape pie charts & heat maps as visualization tools [4]. It provides data related to COVID-19 cases, cases distribution by age, clinical status, and weekly number of cases notified in Italy by region/province. This dashboard also was not fitted on a single screen.

```{r, fig.cap="Italy COVID-19 Dashboard"}
knitr::include_graphics("Images/10.PNG")
```

Live COVID-19 dashboard developed & contributed by an amber innovations for the government of Jamaica has added interactive country map & data table to represent the COVID-
19 cases by parish [9]. Line charts & bar charts have been added to the dashboard for cumulative & daily COVID-19 cases. Yellow, green & red colors have been used to represent confirmed, recovered & deaths respectively. Doughnut shape pie chart has been added to represent the distribution of recovered, confirmed & deaths by age group. This dashboard was not fitted on a single screen.

```{r, fig.cap="Jamaica COVID-19 Dashboard"}
knitr::include_graphics("Images/11.PNG")
```

The GCI COVID-19 dashboard for Russia includes an interactive map, bar charts & line charts to visualize the COVID-19 data [13]. Yellow, green, red & blue colors have been added to
identify the confirmed, recovered, deaths & active case respectively in plotting the charts.

```{r, fig.cap="GCI COVID-19 Dashboard for Russia"}
knitr::include_graphics("Images/12.PNG")
```

COVID-19 live situation analysis dashboard of Sri Lanka contains total & daily figures in Sri Lanka as counts [5]. Total cases & active cases have been visualized by using a line chart. Bar charts have been used to summarize the daily confirmed cases and recovered cases. As well fatality rate, recovery rate & daily investigations using PCR tests & rapid antigen tests have been compared by using the bar charts. Doughnut shape pie chart has been used to summarize the total cases. Blue, green & red colors have been applied to active, recovered & deaths respectively. This dashboard was also not fitted on a single screen.

```{r, fig.cap="COVID-19 Live Situational Analysis Dashboard of Sri Lanka"}
knitr::include_graphics("Images/13.PNG")
```

COVID-19 live situation analysis dashboard of Sri Lanka contains total & daily figures in Sri Lanka as counts [5]. Total cases & active cases have been visualized by using a line chart. Bar charts have been used to summarize the daily confirmed cases and recovered cases. As well fatality rate, recovery rate & daily investigations using PCR tests & rapid antigen tests have been compared by using the bar charts. Doughnut shape pie chart has been used to summarize the total cases. Blue, green & red colors have been applied to active, recovered & deaths respectively. This dashboard was also not fitted on a single screen.

```{r, fig.cap="COVID 19 ZA South Africa Dashboard"}
knitr::include_graphics("Images/14.PNG")
```

Robert Koch-Institute COVID-19 dashboard for German contains interactive map, line charts & bar charts as visualization tools of COVID-19 data [12]. The dashboard has been fitted
on a single screen. This dashboard format is similar to the John Hopkins dashboard.

```{r, fig.cap="Robert Koch-Institute COVID-19 dashboard for German"}
knitr::include_graphics("Images/15.PNG")
```

>>>>

@@

```{r, comment=NA, message=FALSE, warning=FALSE, fig.cap="Spatial DIstribution of COVID1-19 Cases by Districts", fig.height=8}

@@

The "Sri Lanka COVID-19 Dashboard" provides an overview of the COVID-19 pandemic and administration of vaacine information in Sri Lanka.  This dashboard has eight panels as listed in Table 6.

```{r, echo=FALSE, fig.cap="Screeshot of Panel 1", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image1.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 2", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image2.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 3", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image3.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 4", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image4.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 5", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image5.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 6", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image6.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 7", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image7.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 8", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image8.png")
```

@@

### 2022-05-15 manuscript_covid19dashboard.tex
Updated page with images

Table 03 summarizes the visualization methods used in the dashboards. In
almost every dashboard, value boxes have been used to represent these
total figures. Bar charts and line charts (trend lines) are most
frequently used to visualize this data (confirmed cases, recovered
cases, deaths, and vaccination details) with respect to time. A majority
of dashboards presented data either daily or weekly. The mapping is used
to track the spatial distribution of COVID-19 cases by country,
province, regional etc. When visualizing the data by the map color code
system, circles with respect to the size of the cases have been used to
visualize the variation in size. The considerable number of dashboards
has been used in doughnut-shaped pie charts to represent total COVID-19
confirmed cases, recovered cases, active cases, and deaths as a
percentage. Also, region, gender, age group, and ethnicity can be
identified as common breakdowns of COVID-19 cases. Data tables for
representing case~distribution by province/region have been added to
some dashboards. Very few dashboards have been visualized in the
COVID-19 test details. Only 6 dashboards have been compared to global
situations. In addition, the fatality rate, incidence rate, ICU beds,
stage of the patients, and hospitalized details have been contained in
the several dashboards.\hfill\break

@@

@@

The ``Sri Lanka COVID-19 Dashboard'' provides an overview of the
COVID-19 pandemic and administration of vaacine information in Sri
Lanka. Figure 1 shows an screenshot of the dashboard. This dashboard has
eight panels as listed in Table 6. The deployed dashboard is made
accessible to public through
\url{https://thiyanga.netlify.app/post/covid19srilankadb/}

{\centering \includegraphics[width=0.8\linewidth]{images/dashboard}

\caption{Overview Panel: Screeshot of the Dashboard}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Distribution of COVID19 Cases by Districts: (A) Plotted on a
Single Panel, (B) Plotted on Separate Panels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{(A) Global View of Distribution of COVID19 Cases by DIstricts,
(B) Local View of Distribution of COVID19 Cases by Districts}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Spatial DIstribution of COVID1-19 Cases by Districts}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{Images/d3}

@@

\caption{Time Series Plot of Distribution of First Dose and Second Dose}\label{fig:unnamed-chunk-6}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{Images/d2}

@@

\caption{Distribution of Vaccines by Different Types and Dose}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\hypertarget{appendix-overview-of-reviewed-dashboard}{%
\section{Appendix: Overview of reviewed
dashboard}\label{appendix-overview-of-reviewed-dashboard}}

Real time updated COVID-19 dashboard created by the John Hopkins
University Center for Systems Science \& Engineering (JHU CSSE) has
included total confirmed cases \& total deaths by country,
province/region/state (not for all countries){[}6{]}. Weekly \& daily
global confirmed cases, deaths \& vaccine doses have been visualized
using bar plots related to the date in the side panels. Also, an
interactive world map has included in the dashboard to represent total
confirmed cases, incidence rate, fatality ratio \& vaccine doses
administered by country \& state of US. All the links related to the
data sets has been included in the dashboard. In this dashboard red,
white, green colors has been used to indicate confirmed cases, deaths \&
vaccine doses respectively. The dashboard has fitted on a single screen.

\begin{figure}
\includegraphics[width=8.42in]{Images/1} \caption{Johns Hopkins University COVID-19 Dashboard}\label{fig:unnamed-chunk-8}
\end{figure}

Live updated ``WHO COVID-19 dashboard'' contained four panels. The
interactive world map in the dashboard has visualized the distribution
of COVID-19 confirmed cases, deaths \& vaccination by country {[}15{]}.
Line chart \& bar charts have been used as visualization plots. Blue,
red, green colors have been used to represent confirmed cases, deaths \&
vaccination respectively. The links related to the underlying data was
available in the dashboard. The dashboard was not fitted on a single
screen.

\begin{figure}
\includegraphics[width=8.35in]{Images/2} \caption{WHO COVID-19 Dashboard}\label{fig:unnamed-chunk-9}
\end{figure}

The ``COVID-19 surveillance dashboard'' created by the University of
Virginia in collaboration with Bio complexity Institute has included
interactive world map with a time slide to visualize the confirmed
cases, recovered cases, deaths, active cases \& vaccine details {[}7{]}.
Line charts, bar charts \& data tables have been visualized in the
dashboard. Red, blue, green \& yellow colors have been used to identify
confirmed, deceased, recovered \& active cases respectively. The data
behind the dashboard also available on the dashboard \& can be
downloaded. The dashboard has fitted on a single screen.

\begin{figure}
\includegraphics[width=8.42in]{Images/3} \caption{COVID-19 Surveillance Dashboard}\label{fig:unnamed-chunk-10}
\end{figure}

Corona cases (COVID-19) per municipality in Belgium dashboard has
included interactive map for distribution of total confirmed cases per
municipality, bar chart for number of cases per province, line charts
for number of cases per day by region \& municipality, dodge bar chart
for deaths per region, per age \& pie chart for deaths per age as
visualization methods{[}3{]}. Also it included several value boxes for
total cases, total deaths \& hospital situations. There was no specific
color theme used in this dashboard. This dashboard also fitted on a
single screen.

\begin{figure}
\includegraphics[width=8.39in]{Images/4} \caption{Corona cases per Municipality in Belgium Dashboard}\label{fig:unnamed-chunk-11}
\end{figure}

The COVID-19 dashboard for England created by NHS providers included
daily totals, daily changes \& weekly changes in new cases, hospital
admission, patients in hospital, and patients in ICU beds, deaths \&
vaccinations in England as counts {[}2{]}. Bar plots for daily new
cases, hospital admissions \& deaths for last 30 days have been added in
this dashboard. Also it has included data table for total count, daily
changes (as increase or decrease), weekly changes (as increase or
decrease) of new cases \& hospital admission by region. It can be seen
that, three different colors have been used in bar plot as orange for
new cases, green for hospital admissions \& red for deaths. These plots
were not interactive plots \& there was only one panel. The dashboard
was not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.46in]{Images/5} \caption{COVID-19 dashboard for England}\label{fig:unnamed-chunk-12}
\end{figure}

The Environmental Science and Research Institute COVID-19 dashboard for
New Zealand (was developed \& is maintained in collaboration with
Epi-interactive Ltd) contained five panels as overview, outbreak,
source, international \& ESR reports {[}10{]}. In this real time updated
dashboard, they have included value boxes for total confirmed cases,
recovered cases, deaths \& interactive map has been added for
distribution of confirmed \& probable cases as incidence \& count. Also
they have included bar charts for confirmed cases distribution by
gender, age group, \& line charts for confirmed \& deaths as daily \&
cumulative. The dashboard has not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.47in]{Images/6} \caption{New Zealand COVID-19 Dashboard}\label{fig:unnamed-chunk-13}
\end{figure}

Pakistan's official COVID-19 dashboard is a real time updated dashboard
with one panel. This dashboard contains value boxes for total confirmed
cases, active cases, deaths, recovered cases by country. Province wise
cases have been represented by map \& data table {[}11{]}. Line charts
\& bar charts have been added to visualize the distribution of cases
related to time \& province. In the value boxes blue, orange, pink \&
green colors have been applied for confirmed cases, active cases, deaths
\& recoveries respectively, but there was no specific color theme used
when plotting the graphs. The dashboard cannot be seen on a single
screen without grid overlay.

\begin{figure}
\includegraphics[width=8.33in]{Images/7} \caption{COVID-19 Dashboard for Pakistan}\label{fig:unnamed-chunk-14}
\end{figure}

COVID-19 Canada live dashboard has been developed with three panels for
provincial data, hospital resources \& projections {[}14{]}. This
dashboard contained interactive map for represented total reported cases
\& deaths by province. Data tables, line charts, bar charts were the
most frequently used visualization types of this dashboard. More details
were presented on this dashboard by province like ventilator counts,
hospital beds per 100 residents, resource capacity based on critical
case rate, effect of social distance, forecast of deaths \& cases. There
was no specific color theme applied for plotting the graphs. The
dashboard also was not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.47in]{Images/8} \caption{COVID-19 in Canada dashboard}\label{fig:unnamed-chunk-15}
\end{figure}

``Zoho analytics COVID-19 live dashboard'' for India contained three
panels as insight by state, trend analysis \& vaccination {[}1{]}.
Interactive country map has been used to visualize the distribution of
confirmed cases, active cases, deaths, recovered cases \& vaccination by
states in India. Line charts, bar charts \& doughnut shape pie charts
have been used as other visualization tools. Also this dashboard
contained data table for overview of COVID-19 in India. This dashboard
also was not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.42in]{Images/9} \caption{India COVID-19 Dashboard}\label{fig:unnamed-chunk-16}
\end{figure}

Italy COVID-19 dashboard created by the COVID-19 task force of the
department of infection diseases and the IT service Istituto Superiore
Sanita, contained interactive map, bar charts, doughnut shape pie charts
\& heat maps as visualization tools {[}4{]}. It provides data related to
COVID-19 cases, cases distribution by age, clinical status, and weekly
number of cases notified in Italy by region/province. This dashboard
also was not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.12in]{Images/10} \caption{Italy COVID-19 Dashboard}\label{fig:unnamed-chunk-17}
\end{figure}

Live COVID-19 dashboard developed \& contributed by an amber innovations
for the government of Jamaica has added interactive country map \& data
table to represent the COVID- 19 cases by parish {[}9{]}. Line charts \&
bar charts have been added to the dashboard for cumulative \& daily
COVID-19 cases. Yellow, green \& red colors have been used to represent
confirmed, recovered \& deaths respectively. Doughnut shape pie chart
has been added to represent the distribution of recovered, confirmed \&
deaths by age group. This dashboard was not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.35in]{Images/11} \caption{Jamaica COVID-19 Dashboard}\label{fig:unnamed-chunk-18}
\end{figure}

The GCI COVID-19 dashboard for Russia includes an interactive map, bar
charts \& line charts to visualize the COVID-19 data {[}13{]}. Yellow,
green, red \& blue colors have been added to identify the confirmed,
recovered, deaths \& active case respectively in plotting the charts.

\begin{figure}
\includegraphics[width=8.25in]{Images/12} \caption{GCI COVID-19 Dashboard for Russia}\label{fig:unnamed-chunk-19}
\end{figure}

COVID-19 live situation analysis dashboard of Sri Lanka contains total
\& daily figures in Sri Lanka as counts {[}5{]}. Total cases \& active
cases have been visualized by using a line chart. Bar charts have been
used to summarize the daily confirmed cases and recovered cases. As well
fatality rate, recovery rate \& daily investigations using PCR tests \&
rapid antigen tests have been compared by using the bar charts. Doughnut
shape pie chart has been used to summarize the total cases. Blue, green
\& red colors have been applied to active, recovered \& deaths
respectively. This dashboard was also not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.4in]{Images/13} \caption{COVID-19 Live Situational Analysis Dashboard of Sri Lanka}\label{fig:unnamed-chunk-20}
\end{figure}

COVID-19 live situation analysis dashboard of Sri Lanka contains total
\& daily figures in Sri Lanka as counts {[}5{]}. Total cases \& active
cases have been visualized by using a line chart. Bar charts have been
used to summarize the daily confirmed cases and recovered cases. As well
fatality rate, recovery rate \& daily investigations using PCR tests \&
rapid antigen tests have been compared by using the bar charts. Doughnut
shape pie chart has been used to summarize the total cases. Blue, green
\& red colors have been applied to active, recovered \& deaths
respectively. This dashboard was also not fitted on a single screen.

\begin{figure}
\includegraphics[width=8.46in]{Images/14} \caption{COVID 19 ZA South Africa Dashboard}\label{fig:unnamed-chunk-21}
\end{figure}

Robert Koch-Institute COVID-19 dashboard for German contains interactive
map, line charts \& bar charts as visualization tools of COVID-19 data
{[}12{]}. The dashboard has been fitted on a single screen. This
dashboard format is similar to the John Hopkins dashboard.

\begin{figure}
\includegraphics[width=8.33in]{Images/15} \caption{Robert Koch-Institute COVID-19 dashboard for German}\label{fig:unnamed-chunk-22}
\end{figure}

>>>>

Table 03 summarizes the visualization methods used in the dashboards. In
almost every dashboard, value boxes have been used to represent these
total figures. Bar charts and line charts (trend lines) are most
frequently used to visualize this data (confirmed cases, recovered
cases, deaths, and vaccination details) with respect to time. A majority
of dashboards presented data either daily or weekly. The mapping is used
to track the spatial distribution of COVID-19 cases by country,
province, regional etc. When visualizing the data by the map color code
system, circles with respect to the size of the cases have been used to
visualize the variation in size. The considerable number of dashboards
has been used in doughnut-shaped pie charts to represent total COVID-19
confirmed cases, recovered cases, active cases, and deaths as a
percentage. Also, region, gender, age group, and ethnicity can be
identified as common breakdowns of COVID-19 cases. Data tables for
representing case distribution by province/region have been added to
some dashboards. Very few dashboards have been visualized in the
COVID-19 test details. Only 6 dashboards have been compared to global
situations. In addition, the fatality rate, incidence rate, ICU beds,
stage of the patients, and hospitalized details have been contained in
the several dashboards.\hfill\break

@@

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Distribution of COVID19 Cases by Districts: (A) Plotted on a
Single Panel, (B) Plotted on Separate Panels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{(A) Global View of Distribution of COVID19 Cases by DIstricts,
(B) Local View of Distribution of COVID19 Cases by Districts}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Spatial DIstribution of COVID1-19 Cases by Districts}
\end{figure}

@@

The ``Sri Lanka COVID-19 Dashboard'' provides an overview of the
COVID-19 pandemic and administration of vaacine information in Sri
Lanka. This dashboard has eight panels as listed in Table 6.

@@

@@

{\centering \includegraphics[width=0.8\linewidth]{Images/image1}

@@

\caption{Screeshot of Panel 1}\label{fig:unnamed-chunk-5}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{Images/image2}

@@

\caption{Screeshot of Panel 2}\label{fig:unnamed-chunk-6}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/image3}

\caption{Screeshot of Panel 3}\label{fig:unnamed-chunk-7}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/image4}

\caption{Screeshot of Panel 4}\label{fig:unnamed-chunk-8}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/image5}

\caption{Screeshot of Panel 5}\label{fig:unnamed-chunk-9}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/image6}

\caption{Screeshot of Panel 6}\label{fig:unnamed-chunk-10}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/image7}

\caption{Screeshot of Panel 7}\label{fig:unnamed-chunk-11}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{Images/image8}

\caption{Screeshot of Panel 8}\label{fig:unnamed-chunk-12}
\end{figure}

@@
